\setlength\parindent{0pt}

\customsection*{Collaboration} %  and Funding
% My future research vision requires collaboration with expert researchers in many fields, including natural language processing, computer vision, machine learning, data mining, social science, human computer interaction, systems and databases. 
%%
% Past Colab experience
I gained extensive expertise in overseeing and directing major projects, encompassing teams of over 12 individuals and collaborating with various universities and institutions.
I led multiple masters and undergraduate students, collaborated with multiple Ph.D. students and coordinated with 5 professors from different universities to participate in the REALM project. I am fortunate to have close collaborations with professors from multiple universities and research institutes, such as Massachusetts Institute of Technology (MIT), University of Michigan (UMichigan), University of Southern California (USC), Information Sciences Institute (ISI), Institute for Defense Analyses (IDA), University of Massachusetts (UMass), Middle East Technical University (METU), etc. I also have had the fortune to work closely with researchers from computer vision, NLP, databases, systems, and applications, along with end-users and program managers to conduct interdisciplinary research. 
%
%
% Future Colab
%
%
% I intend to maintain my current collaborations while actively cultivating new partnerships to advance the establishment of robust principles that underpin research in multimodal knowledge and novelty in learning models.

%
To realize my future research vision, I plan to collaborate with accomplished researchers from various disciplines, such as natural language processing, computer vision, machine learning, data mining, social science, human-computer interaction, systems, and databases. 
% -------------- Next line would be replaced with custom values -------------------
% This collaborative effort extends to CWU, where I anticipate collaborating with experts like Szilárd Vajda, Boris Kovalerchuk, and others. 
% Li Yang, Ajay Gupta, Guan Yue Hong, Alvis fong, and others
This collaborative effort extends to \shortInstitutionName{}, where I anticipate collaborating with experts like Li Yang (Data aggregation and Data embedding), Ajay Gupta (Decision making, Data Privacy, and Smart buildings), Guan Yue Hong, Alvis Fong (Information Retrieval and Multimedia data), and others. With Li Yang, I can extend my work on Data Fusion and Representation Learning. I can collaborate with Ajay Gupta on building explainable and robust decision-making agents and privacy-preserving data dissemination. Guan Hong can work with me on intelligent systems and contextual reasoning-based agents. I can complement Hong's contributions with multimodal data processing and novelties in learning algorithms.
%
%
Additionally, I aim to establish connections with researchers from other 
% predominantly undergraduate institutions and research 
institutions beyond \shortInstitutionName{} to advance the establishment of robust principles that underpin research in multimodal knowledge and novelty in learning models. 

\customsection*{Funding}
% Past funding 
During my Ph.D., my work has been supported by Northrop Grumman Corporation (NGC), 
% Research Consortium for Artificial Intelligence and Machine Learning
DARPA, ARFL, and Sandia National Lab. 
% Additionally, I have contributed significantly to the writing of grant proposals, including idea
% generation, method design, idea illustration and visual aid creation, such as 
% % DARPA KAIROS project,
% DARPA ITM project, and DARPA Triage Challenge.
Additionally, I have made substantial contributions to the development of grant proposals, which involved various aspects such as generating ideas, designing methodologies, illustrating ideas, and creating visual aids to support the proposals. Notably, I have contributed to proposals such as the DARPA ITM project and the DARPA Triage Challenge.

%%%%%%%%%%%%%% Funding I will pursue
For my future proposals, %at \shortInstitutionName{}, 
I will be designing them as clearly articulated and doable projects with clearly formulated hypotheses and research questions, and a definitive plan for implementation with clear milestones. 
As a future faculty, I will continue to seek funding opportunities % in the future 
from early career supports, and various funding agencies %(e.g., DARPA, ARL, AFRL, IARPA, NSF, NIH, DOE, DOD) 
and industries, including NGC, Microsoft, IBM, Ford, Meta, Google, Intel, while collaborating with recognized experts and colleagues from my research areas.
Specifically, I will aim for NSF CAREER, CRII, EAGER, and ADVANCE awards, OSR young investigator programs from DOE, DARPA, AFRL, NASA, and other research awards. 


% CISE .nsf.gov

% Ford alliance

% Sandia labs

% AFRL norm Ahmed mark linderman

% NGC Jason Kobe’s

% PLM manufacturing center

% Career award training at Purdue

% Talk some ML and AI for security or other directions