% For undergraduate students, I would be happy to teach the fundamental courses, including %structured and object-oriented
% programming languages, introductory programming, data structures and algorithms, discrete mathematics, theory of computation, data science, and computer graphics. 
% As a prospective teacher, I am also excited to offer software engineering, databases, networks, compilers, information retrieval, data management systems, and machine learning courses. 
For undergraduate students, I am enthusiastic about teaching essential courses such as programming languages, introductory programming, data structures and algorithms, discrete mathematics, theory of computation, data science, and computer graphics. Additionally, as an aspiring instructor, I am eager to provide courses in software engineering, databases, networks, compilers, information retrieval, data management systems, and machine learning. Furthermore, I have plans to introduce courses focused on multimodal information retrieval and adaptable and explainable AI for students interested in research. These courses will be based on recent papers from top conferences in machine learning, information retrieval, OpenAI, and XAI. The course projects will be designed to facilitate potential publications and simulate peer reviewing processes.
Moreover, I have plans to offer courses related to multimodal information retrieval and adaptable and explainable AI to students with a research interest. 
These courses will be based on recently published papers in top conferences in machine learning, information retrieval, OpenAI, and XAI conferences. The course projects will be designed in a way that can lead to publications and can mimic peer reviewing. 
%

% what courses you would develop new to the curriculum%%%%%
Besides that, I would also like to extend the current curriculum based on my research experience with \textit{``Applied Machine Learning for Open World Systems"}. Tentative topics include data cleaning, handling lack of annotations, scalability, weakly supervised learning, multimodal information retrieval and feature extraction, intrinsic and extrinsic complexity of system domains, and case study of real-world use cases. Since learning algorithms must be adaptive to real-world situations, it will also include detection, adaptation, and difficulty analysis of novelties in machine learning algorithms.
