% -- Seminar courses: Realm, SAIL-on, mmmir\\
% ug course, graduate courses, & seminar courses
I am excited to teach both undergraduate and graduate-level students. I am comfortable teaching software engineering, databases, networks, compilers, information retrieval, data management systems (SQL and NoSQL systems), and machine learning courses to both undergraduate and graduate students. I know the differences between them from my teaching experience at both levels.
For undergraduate students, I would be happy to teach core courses, including %structured and object-oriented
programming languages, data structure, theory of computation, and computer graphics. Specifically, for graduate students, I can offer advanced information retrieval, natural language processing, distributed database systems, data science, or data mining.
% compiler, software development, programming language,
% I took graduate level Compiling and Programming Systems in Fall'22, and am familiar with llvm
%
Moreover, I have plans to offer seminar courses related to multimodal information retrieval and adaptable and explainable AI to students with a research interest. 
These courses will be based on recently published papers in top conferences in machine learning, information retrieval, OpenAI, and XAI conferences. The course projects will be designed in a way that can lead to publications and can mimic peer reviewing. 
%

% what courses you would develop new to the curriculum
Besides that, I would also like to create a new course \textit{``Applied Machine Learning for Open World Systems"} to extend the current curriculum based on my research experience. Tentative topics would include data cleaning, 
% (e.g., multi-tenancy, storage/compute separation, machine learning as a service), 
handling lack of annotations, scalability,
% jiungo statemnt 
% systems aspects of data science for large-scale data. databases (e.g., query processing, storage, transaction), distributed databases (e.g., consensus, consistency, availability), NoSQL systems (e.g., key-value stores, search engine systems),
weakly supervised learning, multimodal information retrieval and feature extraction, intrinsic and extrinsic complexity of system domains, and case study of real-world use cases. Since learning algorithms must be adaptive to real-world situations, it will also include detection, adaptation, and difficulty analysis of novelties in machine learning algorithms.