\customsection*{Collaboration and Funding}
My future research vision requires collaboration with expert researchers in many
fields, including natural language processing, computer vision, machine learning, data mining, social science, human computer interaction, systems and databases. 
%%
I gained extensive expertise in overseeing and directing major projects, encompassing teams of over 12 individuals and collaborating with various universities and institutions.
I led multiple masters and undergraduate students, collaborated with multiple Ph.D. students and coordinated with 5 professors from different universities to participate in the REALM project. I am fortunate to have close collaborations with professors from multiple universities and research institutes, such as Massachusetts Institute of Technology (MIT), University of Michigan (UMichigan), University of Southern California (USC), Information Sciences Institute (ISI), Institute for Defense Analyses (IDA), University of Massachusetts (UMass), Middle East Technical University (METU), etc. I also have had the fortune to work closely with researchers from databases and applications, along with end-users and program managers to conduct interdisciplinary research. 
% I plan to continue existing collaborations and foster new connections in order to develop well-established principles underlying multimodal knowledge and novelty in learning models research.
I intend to maintain my current collaborations while actively cultivating new partnerships to advance the establishment of robust principles that underpin research in multimodal knowledge and novelty in learning models.

During my Ph.D., my work has been mainly supported by the Northrop Grumman Corporation (NGC), 
% Research Consortium for Artificial Intelligence and Machine Learning
DARPA, ARFL, and Sandia National Lab. 
% I have been nominated by DARPA as a DARPA Riser (awarded to young faculties, postdocs, and senior PhDs who will lead to technological breakthroughs), and I presented ideas directly to DARPA project managers during the invitation-only DARPA Forward Event.
Additionally, I have contributed significantly to the writing of grant proposals, including idea
generation, method design, idea illustration and visual aid creation, such as 
% DARPA KAIROS project,
DARPA ITM project, and DARPA Triage Challenge.
% DARPA SemaFor project, DARPA CCU project, and NSF MMLI project. 
As a future faculty, I will continue to seek funding opportunities in the future from early career supports, various funding agencies (e.g., DARPA, ARL, AFRL, IARPA, NSF, NIH, DOE, DOD) and industries (e.g., NGC, Microsoft, IBM, Ford, Meta, Google, Intel).
Specifically I will aim for NSF CAREER, NSF CRII, NSF EAGER, NSF ADVANCE, OSR young investigator programs from DOE, DARPA, AFRL, NASA, and other research awards.


% CISE .nsf.gov

% Ford alliance

% Sandia labs

% AFRL norm Ahmed mark linderman

% NGC Jason Kobe’s

% PLM manufacturing center

% Career award training at Purdue

% Talk some ML and AI for security or other directions