\noindent\rule{2cm}{4pt}~\textbf{\textsc{Collaboration and Funding.}}
My future research vision requires collaboration with expert researchers in many
fields, including natural language processing, computer vision, machine learning, data mining, social science, human computer interaction, systems and databases at USU. 
%%
With the DSA lab, led by Hamid Karimi, we can expand student modeling by incorporating personalized lesson recommendations and integrating multimodal data analysis into the understanding of user-generated content. Additionally, we can collaborate on enhancing information credibility through tracking, cross-checking with social contexts, and verifying multimodal data.
%
Curtis Dyreson and I can collaborate to develop innovative approaches for managing multimodal and multidimensional database systems.
%
I can work with Soukaina Boubrahimi to integrate multimodal information processing techniques into time series analysis and space weather mining.
%
Considering that Bangladesh is a developing country with potential for HCI-based research, I have been closely following the HCI research conducted at my alma mater. Collaborating with Mahdi Nasrullah Al-Ameen and Isaac Chao would enable us to explore user preference and behavior modeling and understand privacy, trust, and fairness of information in a global context.
%
Shuhan Yuan and I can expand the scope of `hate crime detection' by incorporating videos, images, and text, as well as further develop anomaly detection methods specifically for text.
%
Working with Mario Harper, I can extend my work on decision making in the planning domain and develop learning algorithms that can operate effectively under uncertain conditions.
%
Collaboration with Vicki Allan presents opportunities to explore urban information systems through stochastic path planning for smart cities, as well as investigating collusion in games for manipulation and incorporating recommendation-based trust decision-making.
%
My expertise in multimodal information retrieval and personalized recommendation systems can be extended to educational data mining through collaboration with Isaac Cho, Vicki Allan, and John Edwards.
%
% Additionally, I have an interest in object tracking and could potentially collaborate with Xiaojun Qi in this area.



%%
%%
%%
% I intend to maintain my current collaborations while actively cultivating new partnerships to advance the establishment of robust principles that underpin research in multimodal knowledge and novelty in learning models.

During my Ph.D., my work has been mainly supported by the Northrop Grumman Corporation (NGC), 
% Research Consortium for Artificial Intelligence and Machine Learning
DARPA, ARFL, and Sandia National Lab. 
% I have been nominated by DARPA as a DARPA Riser (awarded to young faculties, postdocs, and senior PhDs who will lead to technological breakthroughs), and I presented ideas directly to DARPA project managers during the invitation-only DARPA Forward Event.
I have contributed significantly to the writing of grant proposals, including idea
generation, method design, idea illustration and visual aid creation, such as 
% DARPA KAIROS project,
DARPA ITM project, and DARPA Triage Challenge.
% DARPA SemaFor project, DARPA CCU project, and NSF MMLI project. 
As a future faculty, I will continue to seek funding opportunities in the future from early career fellowships and various funding agencies (e.g., DARPA, ARL, AFRL, IARPA, NSF, NIH, DOE, DOD) and industries (e.g., NGC, Microsoft, IBM, Ford, Meta, Google, Intel).

% CISE .nsf.gov

% Ford alliance

% Sandia labs

% AFRL norm Ahmed mark linderman

% NGC Jason Kobe’s

% PLM manufacturing center

% Career award training at Purdue

% Talk some ML and AI for security or other directions